## Birthday Problem - Final Script

```{r}
library(tidyverse)
```

## Creating the function

```{r}
birthday_problem<-function(people,iterations=10000,probabilities=rep(1,366)){

matches<-data.frame(rep=1:iterations,match=NA)

for(i in 1:iterations){

birthdays<-sample(1:366,people,replace=TRUE,prob=probabilities)

matches$match[i]<-birthdays %>%
  duplicated() %>%
   max() 
}

matches %>%
  summarise(proportion_matched=mean(match),se=sd(match)/sqrt(iterations),people=people,iterations=iterations) %>%
  return()

}

```


## Reading in the ONS data and modifying the ratio of each birthday to account for leap years
```{r}
uk_births<-read.csv(url("https://www.ons.gov.uk/visualisations/nesscontent/dvc307/line_chart/data.csv")) %>%
  mutate(ratio=ifelse(date=="29-Feb",average/4,average))
```

# Picking out some examples of using the function

```{r}
birthday_problem(10,probabilities=uk_births$ratio)

birthday_problem(10)
```

## Using map_df to loop across 1-100 size parties each 1000 times using equal birthday distribution

```{r}
equal_birthdays<-1:100 %>%
map_df(birthday_problem,iterations=1000)
```


## Using map_df to loop across 1-100 size parties each 1000 times using realistic birthday distribution

```{r}
real_birthdays<-1:100 %>%
map_df(birthday_problem,iterations=1000,probabilities=uk_births$ratio)
```

## Putting it into a nice plot

```{r}
ggplot(equal_birthdays,aes(y=proportion_matched,x=people))+
  geom_line(col="red")+
  geom_line(col="blue",data=real_birthdays)
```





```{r}
sample(1:366,23,replace=TRUE,prob=uk_births$ratio)
```


